# Week 3 Project

## David Shuman

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```

### Deconstructing Graphics

```{r,fig.width=10}
ggplot(data = CPS85, aes(x = exper, y = wage, color = married)) + geom_point() + facet_wrap( ~sector, nrow=2,ncol=4)
```

```{r,fig.width=10}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex, fill=sex),alpha=.3) + facet_wrap(~pregnant)
```

### Wrangling

#### Diamonds

Each of the following tasks can be accomplished by a statement of the form

diamonds %>% 
  verb1( args1 ) %>% 
  verb2( args2 ) %>% 
  arrange(desc( args3 )) %>% 
  head( 1 )
  
1. Which color diamonds seem to be largest on average (in terms of carats)?
```{r}
  diamonds %>%
    group_by(color)%>%
    summarise(avg.size=mean(carat))%>%
    arrange(desc(avg.size))%>%
    head(1)
```

2. Which clarity of diamonds has the largest average “table” per carat?
```{r}
  diamonds%>%
    group_by(clarity)%>%
    summarise(avg.table.per.carat=mean(table/carat))%>%
    arrange(desc(avg.table.per.carat))%>%
    head(1)
```

#### Voting

1. How many cases are there?
```{r}
  Minneapolis2013%>%
    summarise(ncase=n())
```

2. Who were the top 5 candidates in the `Second` vote selections?

```{r}
  Minneapolis2013%>%
    group_by(Second)%>%
    summarise(nvotes=n())%>%
    arrange(desc(nvotes))%>%
    head(5)
```


3. How many ballots are marked “undervote” in
  - First choice selections?
  - Second choice selections?
  - Third choice selections?

```{r}
  Minneapolis2013%>%
    group_by(First)%>%
    summarise(nFirstVotes=n())%>%
    filter(First=="undervote")

  Minneapolis2013%>%
    group_by(Second)%>%
    summarise(nSecondVotes=n())%>%
    filter(Second=="undervote")
  
  Minneapolis2013%>%
    group_by(Third)%>%
    summarise(nThirdVotes=n())%>%
    filter(Third=="undervote")
```
4. What are the top 3 `Second` vote selections among people who voted for Betsy Hodges as their first choice?

```{r}
  Minneapolis2013%>%
    filter(First=="BETSY HODGES")%>%
    group_by(Second)%>%
    summarise(nSecondVotes=n())%>%
    arrange(desc(nSecondVotes))%>%
    head(3)
```

5. Which `Precinct` had the highest fraction of `First` vote selections marked as “undervote”? (To calculate the fraction, use `mean(First == "undervote")` in the argument to `summarise()`.)

```{r}
  Minneapolis2013%>%
    group_by(Precinct)%>%
    summarise(percent.undervote=mean(First == "undervote"))%>%
    arrange(desc(percent.undervote))%>%
    head(1)
```